Personality and political beliefs across the lifespan

### 2019-12-07 scripts/manuscript.tex
Updated References

\section{Methods}\label{methods}

We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

\subsection{Participants}\label{participants}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

\subsection{Data analysis}\label{data-analysis}

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
\emph{dplyr} (Version 0.8.3; Wickham, François, Henry, \& Müller, 2019),
\emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version
3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017),
\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{purrr}
(Version 0.3.3; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1;
Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; C.-h.
Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0;
Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and
\emph{tidyverse} (Version 1.2.1; Wickham, 2017) for all our analyses.

\section{Results}\label{results}

\section{Discussion}\label{discussion}

@@

\section{References}\label{references}

@@

\hypertarget{refs}{}
\hypertarget{ref-R-papaja}{}
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\hypertarget{ref-R-rio}{}
Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018).
\emph{Rio: A swiss-army knife for data file i/o}.

\hypertarget{ref-R-purrr}{}
Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

\hypertarget{ref-R-here}{}
Müller, K. (2017). \emph{Here: A simpler way to find your files}.
Retrieved from \url{https://CRAN.R-project.org/package=here}

\hypertarget{ref-R-tibble}{}
Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
Retrieved from \url{https://CRAN.R-project.org/package=tibble}

\hypertarget{ref-R-base}{}
R Core Team. (2019). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\hypertarget{ref-R-ggplot2}{}
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
Springer-Verlag New York. Retrieved from
\url{https://ggplot2.tidyverse.org}

\hypertarget{ref-R-tidyverse}{}
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
'tidyverse'}. Retrieved from
\url{https://CRAN.R-project.org/package=tidyverse}

\hypertarget{ref-R-forcats}{}
Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
variables (factors)}. Retrieved from
\url{https://CRAN.R-project.org/package=forcats}

\hypertarget{ref-R-stringr}{}
Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
common string operations}. Retrieved from
\url{https://CRAN.R-project.org/package=stringr}

\hypertarget{ref-R-tidyr}{}
Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\hypertarget{ref-R-dplyr}{}
Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
A grammar of data manipulation}. Retrieved from
\url{https://CRAN.R-project.org/package=dplyr}

\hypertarget{ref-R-readr}{}
Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read
rectangular text data}. Retrieved from
\url{https://CRAN.R-project.org/package=readr}

>>>>

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table1}Mean Personality Trait Scores by Social Conservatism Score}
\begin{tabular}{llllll}
\toprule
 & \multicolumn{5}{c}{Social Conservatism Score} \\
\cmidrule(r){2-6}
personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
\midrule
Agreeableness & 4.67 & 5.20 & 4.88 & 5.76 & 5.90\\
Conscientiousness & 5.37 & 5.44 & 5.32 & 5.84 & 6.03\\
Emotional stability & 4.07 & 4.38 & 4.82 & 5.50 & 5.57\\
Extraversion & 2.73 & 3.16 & 3.57 & 3.90 & 3.72\\
Openness to experiences & 4.93 & 5.40 & 5.43 & 5.25 & 5.12\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table2}Mean Personality Trait Scores by Economic Conservatism Score}
\begin{tabular}{llllll}
\toprule
 & \multicolumn{5}{c}{Economic Conservatism Score} \\
\cmidrule(r){2-6}
personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
\midrule
Agreeableness & 6.14 & 5.21 & 5.29 & 5.40 & 5.43\\
Conscientiousness & 5.50 & 5.31 & 5.60 & 5.77 & 6.00\\
Emotional stability & 4.29 & 4.67 & 5.09 & 4.85 & 5.62\\
Extraversion & 2.79 & 3.67 & 3.61 & 3.42 & 3.50\\
Openness to experiences & 6.43 & 5.44 & 5.12 & 5.05 & 5.21\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Social Conservatism From Big-Five Personality Traits.}
\begin{tabular}{lllll}
\toprule
Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
\midrule
Intercept & 25.82 & $[0.07$, $51.58]$ & 1.98 & .049\\
Openness to experiences & -3.73 & $[-7.50$, $0.04]$ & -1.96 & .052\\
Conscientiousness & 0.07 & $[-3.98$, $4.11]$ & 0.03 & .974\\
Extraversion & 1.56 & $[-1.42$, $4.55]$ & 1.04 & .302\\
Agreeableness & 3.93 & $[0.69$, $7.17]$ & 2.40 & .018\\
Emotional stability & 4.30 & $[0.70$, $7.91]$ & 2.37 & .020\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Residual standard error: 25.13 on 125 degrees of freedom.
Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.}
\begin{tabular}{lllll}
\toprule
Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
\midrule
Intercept & 56.54 & $[34.71$, $78.37]$ & 5.13 & < .001\\
Openness to experiences & -3.79 & $[-6.98$, $-0.59]$ & -2.35 & .021\\
Conscientiousness & 1.78 & $[-1.65$, $5.20]$ & 1.03 & .307\\
Extraversion & 0.61 & $[-1.92$, $3.14]$ & 0.48 & .632\\
Agreeableness & -1.13 & $[-3.88$, $1.61]$ & -0.82 & .415\\
Emotional stability & 2.34 & $[-0.71$, $5.39]$ & 1.52 & .131\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Residual standard error: 21.3 on 125 degrees of freedom. Multiple R-squared: 0.081, Adjusted R-squared: 0.044. F(5, 125): 2.207, p-value: 0.058.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

In order to understand the relation between conservatism and personality, we first looked at Big Five personality trait (Openness to Experience, Conscientiousness, Extraversion, Agreeableness, and Emotional Stability) scores across the spectrum of Social Conservatism (Table 1) and Economic Conservatism (Table 2) scores.

To see whether there were significant relations between Social Conservatism and the Big Five, we then ran a multiple regression predicting Social Conservatism from the Big Five personality traits. A significant regression equation was found (\emph{F}(5, 125) = 5.051, \emph{p} \textless{} .001), with an adjusted \(R^2\) of 0.135 (Table 2). Thus, personality traits taken together explained 13.48\% of variance in Social Conservatism scores. Participants' predicted Social Conservatism scores were equal to 25.82 - 3.73(Openness to Experience) + 0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) + 4.30(Emotional Stability). Agreeableness and Emotional Stability were significant predictors of Social Conservatism.

To see whether there were significant relations between Economic Conservatism and the Big Five, we then ran a multiple regression predicting Economic Conservatism from the Big Five personality traits. No significant regression equation was found (\emph{F}(5, 125) = 2.207, \emph{p} = .058) (Table 3). Thus, personality traits taken together did not significantly explain variance in Economic Conservatism scores. However, Openness to Experience was a significant predictor of Economic Conservatism.

To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65. Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\begin{verbatim}
## Warning in readLines(file): incomplete final line found on 'r-
## references.bib'
\end{verbatim}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-rio}{}%
Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.

\leavevmode\hypertarget{ref-R-janitor}{}%
Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}

\leavevmode\hypertarget{ref-R-viridis}{}%
Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}

\leavevmode\hypertarget{ref-R-viridisLite}{}%
Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}

\leavevmode\hypertarget{ref-R-purrr}{}%
Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

\leavevmode\hypertarget{ref-R-here}{}%
Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}

\leavevmode\hypertarget{ref-R-tibble}{}%
Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-R-psych}{}%
Revelle, W. (2018). \emph{Psych: Procedures for psychological, psychometric, and personality research}. Evanston, Illinois: Northwestern University. Retrieved from \url{https://CRAN.R-project.org/package=psych}

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}

\leavevmode\hypertarget{ref-R-forcats}{}%
Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}

\leavevmode\hypertarget{ref-R-stringr}{}%
Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}

\leavevmode\hypertarget{ref-R-dplyr}{}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\leavevmode\hypertarget{ref-R-readr}{}%
Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}

\leavevmode\hypertarget{ref-R-knitr}{}%
Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}

Call:corr.test(x = untidy\(economic_conservatism, y = untidy\)social\_conservatism)
Correlation matrix
{[}1{]} 0.65
Sample Size
{[}1{]} 131
Probability values adjusted for multiple tests.
{[}1{]} 0

To see confidence intervals of the correlations, print with the short=FALSE option

\begin{lltable}

\tiny{
\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:correlations}Correlation Matrix for Conservatism and Big Five Personality Traits}\\
\toprule
 & \multicolumn{1}{c}{Economic conservatism} & \multicolumn{1}{c}{Social conservatism} & \multicolumn{1}{c}{Agreeableness} & \multicolumn{1}{c}{Conscientiousness} & \multicolumn{1}{c}{Openness to experiences} & \multicolumn{1}{c}{Extraversion} & \multicolumn{1}{c}{Emotional stability}\\
\midrule
Economic conservatism & 1 &  &  &  &  &  & \\
Social conservatism & 0.65 & 1 &  &  &  &  & \\
Agreeableness & -0.02 & 0.29 & 1 &  &  &  & \\
Conscientiousness & 0.14 & 0.18 & 0.28 & 1 &  &  & \\
Openness to experiences & -0.15 & -0.02 & 0.2 & 0.18 & 1 &  & \\
Extraversion & 0.02 & 0.17 & 0.2 & 0.12 & 0.44 & 1 & \\
Emotional stability & 0.16 & 0.33 & 0.35 & 0.54 & 0.28 & 0.42 & 1\\
\bottomrule
\end{longtable}
}
\end{lltable}

\includegraphics{manuscript_files/figure-latex/correlations-1.pdf}

\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}

```
